### 2015-05-16 ase-2015-tex/summary-heap.tex
defined r_null, r_un, fresh_l, isInit(), and mathcal{L}

\begin{compactdesc}
\item[Reference partitions:] Each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
  heap}% that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in constraints)
  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
  literals}% that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere)
  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
  literals} %(these appear in environments, expressions, and continuations).
\item[Null and Uninitialized:] Every symbolic heap contains 
two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
  ($\cfgnt{l}_\mathit{un}$) with $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
\item[Immutability:] References do not change once added to the
location map, eliminating any need for constraint rewriting as the program state evolves.
\item[Determinism:] A reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
$
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
$
where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
\item[Type consistency:] All locations associated with a reference have the same type:
$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$

@@

Other more complex rules, such as one to create a new instance of a
class, define constraints on the rewrites and more complex
transformations on the heap.
$$
\mprset{flushleft}
	\inferrule[New]{
      \cfgnt{r} = \mathrm{stack}_r\lp \rp\\
      l = \mathrm{fresh}_l\lp \cfgnt{C}\rp\\\\
      \cfgnt{R}^\prime = \cfgnt{R}[\forall \cfgnt{f} \in \mathit{fields}\lp \mathrm{C}\rp \ \lp \lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}_\mathit{null} \rp ] \\\\
      \cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}]
    }{
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgt{new}\ \cfgnt{C}\rp \ \cfgnt{k}\rp  \rcom
      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi\ \eta\ \cfgnt{r}\ \cfgnt{k}\rp 
	}
$$ In this rule, when the string matches the new-expression, it is
        rewritten to use a new heap location where all of the fields
        for the new object point to $\cfgnt{r}_\mathit{null}$ and the
        location map points a new stack reference to that new object.
        Note that references for objects from the new-expression are
        auxiliary literals, so they do not appear in any constraint in
        the symbolic heap as an aliasing option.

>>>>

\begin{compactdesc}
\item[Reference partitions:] Each reference belongs to one of three partitions: $\mathrm{init}_\cfgnt{r}()$ for the \emph{input
  heap}% that includes $\cfgnt{r}_\mathit{null}$ (these are created by lazy initialization and are the only references that appear as variables in constraints)
  ; $\mathrm{fresh}_\cfgnt{r}()$ for \emph{auxiliary
  literals}% that includes $\cfgnt{r}_\mathit{un}$ (these add structure but do not appear elsewhere)
  ; and $\mathrm{stack}_\cfgnt{r}()$ for \emph{stack
  literals}. %(these appear in environments, expressions, and continuations).
  Only input heap references appear in constraints to express potential aliasing.
  Auxiliary literals and stack references are used to define additional structure in the bipartite graph but only stack references can appear in environments, expressions, or continuations.
\item[Null and Uninitialized:] Every symbolic heap contains 
two special locations, null ($\cfgnt{l}_\mathit{null}$), and uninitialized,
  ($\cfgnt{l}_\mathit{un}$)  with corresponding references 
  $\cfgnt{r}_\mathit{null}$ and $\cfgnt{r}_\mathit{un} 
  where $\cfgnt{L}(\cfgnt{r}_\mathit{null}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{null})\}$ and
  $\cfgnt{L}(\cfgnt{r}_\mathit{un}) =
  \{(\cfgt{true}\ \cfgnt{l}_\mathit{un})\}$. 
\item[Immutability:] References do not change once added to the
location map, eliminating any need for constraint rewriting as the program state evolves.
\item[Determinism:] A reference in $(\cfgnt{L}\ \cfgnt{R})$ cannot point to multiple locations simultaneously: 
$
\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\cfgnt{l} \neq \cfgnt{l}^\prime \vee \phi \neq \phi^\prime) \Rightarrow (\phi \wedge \phi^\prime = \cfgt{false}))
$
where $\cfgnt{L}^\leftarrow$ is the pre-image of $\cfgnt{L}$. 
\item[Type consistency:] All locations associated with a reference have the same type:
$\forall \cfgnt{r} \in \cfgnt{L}^\leftarrow\ (\forall (\phi\ \cfgnt{l}),(\phi^\prime\ \cfgnt{l}^\prime) \in \cfgnt{L}(r)\ (
(\mathrm{Type}\lp\cfgnt{l}\rp = \mathrm{Type}\lp\cfgnt{l}^\prime\rp)))$

@@

Other more complex rules, such as one to create a new instance of a
class, define constraints on the rewrites and more complex
transformations on the heap.
$$
\mprset{flushleft}
	\inferrule[New]{
      \cfgnt{r} = \mathrm{stack}_r\lp \rp\\
      l = \mathrm{fresh}_l\lp \cfgnt{C}\rp\\\\
      \cfgnt{R}^\prime = \cfgnt{R}[\forall \cfgnt{f} \in \mathit{fields}\lp \mathrm{C}\rp \ \lp \lp l\ \cfgnt{f}\rp  \mapsto \cfgnt{r}_\mathit{null} \rp ] \\\\
      \cfgnt{L}^\prime = \cfgnt{L}[\cfgnt{r} \mapsto \{\lp \cfgt{true}\ l\rp \}]
    }{
      \lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \lp \cfgt{new}\ \cfgnt{C}\rp \ \cfgnt{k}\rp  \rcom
      \lp \cfgnt{L}^\prime\ \cfgnt{R}^\prime\ \phi\ \eta\ \cfgnt{r}\ \cfgnt{k}\rp 
	}
$$ In this rule, when the string matches the new-expression, it is
        rewritten to use a new heap location where all of the fields
        for the new object point to $\cfgnt{r}_\mathit{null}$ and the
        location map points a new stack reference to that new object.
        New heap locations returned from \mathrm{fresh}_l are monotonically
        increasing.
        Also note that references for objects from the new-expression are
        auxiliary literals, so they do not appear in any constraint in
        the symbolic heap as an aliasing option.
